Introduction to LLL\\``Cryptography''

### 2021-05-26 paper.tex
Add SVP and CVP

\begin{theorem}
    \textbf{Gram-Schmidt Algorithm}
\end{theorem}

@@

\begin{figure}[!tbp]
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b0.png}
        \caption{Lattice $L$ of $v, w$}
        \label{fig:lattice0}
    \end{minipage}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b1.png}
        \caption{Lattice $L$ of $v', w'$}
        \label{fig:lattice1}
    \end{minipage}
\end{figure}

>>>>

\begin{algorithm}
    \textbf{Gram-Schmidt Algorithm}
\end{algorithm}

@@

\begin{figure}[!tbp]
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b0.png}
        \caption{Lattice $L$ spanned by $v, w$}
        \label{fig:lattice0}
    \end{minipage}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \hspace{\fill}
    \begin{minipage}[b]{0.50\textwidth}
        \includegraphics[width=\textwidth]{./img/lattice_b1.png}
        \caption{Lattice $L$ spanned by $v', w'$}
        \label{fig:lattice1}
    \end{minipage}
\end{figure}

\section{Problems}

\subsection{SVP}

\textbf{The Shortest Vector Problem} (\texttt{SVP}): Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.

\begin{algorithm}
    \textbf{Gauss Reduction}
\end{algorithm}

Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.

If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.

\begin{figure}[b]
    \centering
    \includegraphics[width=0.5\textwidth]{./img/gauss_svp.png}
    \caption{Gauss reduction}
    \label{fig:gauss_svp}
\end{figure}

However the bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.

\subsection{CVP}

\textbf{The Closest Vector Problem} (\texttt{CVP}): Given a vector $w \in \R^m$ that is not in $L$, find a vector $v \in L$ that is closest to $w$,
in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert w - v \rVert$.

Example in \ref{fig:cvp}

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{./img/cvp.png}
    \caption{CVP}
    \label{fig:cvp}
\end{figure}
